---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# corrplot

<!-- badges: start -->
<!-- badges: end -->

The purpose of `corrplot` is to provide a easy way for exploring the relationship between two variables. It will plot a scatter plot and show the correlation coefficients.

## Installation

You can install the released version of corrplot from [github](https://github.com/wu-2018/corrplot) with:

``` r
install.packages("devtools")
devtools::install_github("wu-2018/corrplot")
```

## Example

```{r example}
library(corrplot)
```

Use the iris dataset for example:

```{r}
correlation_scatter(datasets::iris, x='Sepal.Length', y='Sepal.Width', group='Species', cor_method = "pearson")
```

It creates a scatter plot showing the relationship between `Sepal.Length` and `Sepal.Length`, grouped by the factor `Species`. Note the correlation coefficients are annotated.  



